### 2013-06-03 doc/nips2013/mixture.tex

We need to specify conditions on the transformation function $\phix$
to ensure that enough information is retained to pinpoint the parameters later.
The following condition characterizes $\phix$:
\begin{property}
  \label{property:transformation}
  The transformation $\phix$ (chosen by us) is such that $C \eqdef
  (\E[\philocal(x_j, h) \mid h])_{h \in [\nh]} \in \R^{d \times h}$ is a
  function of $B$.
\end{property}
Here, $C$ provide a view on the local features $\philocal(x_j,h)$,
which are
closely related to the model parameters \refeqn{mixtureModel},
and $B$ is what we have recovered so far.
%Note that we couldn't recover $C$ directly because it depends on $h$.

>>>>

We need to specify conditions on the transformation function $\phix$
to ensure that enough information is retained to pinpoint the parameters later.
The following condition characterizes $\phix$:
\begin{property}
  \label{property:transformation}
  The transformation $\phix$ (chosen by us) is such that $C \eqdef
  (\E[\philocal(x_j, h) \mid h])_{h \in [\nh]} \in \R^{d \times h}$ is a
  function of $B$.
\end{property}
Here, $C$ provides a view on the local features $\philocal(x_j,h)$,
which are
closely related to the model parameters \refeqn{mixtureModel},
and $B$ is what we have recovered so far.
%Note that we couldn't recover $C$ directly because it depends on $h$.
